---
title: "Assignment5"
author: "Tanvi Arora"
date: "June 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question1 - Data Munging \

Dataset used  - yob2016.txt \
Description   - This file is a series of popular children's names born in the year 2016 in the United States. \
variables     - firstname,gender,amount of children given that name \

```{r datamunging,echo=TRUE}
# 1.a import given dataset into R dataframe df

df <- read.table('Data/yob2016.txt', sep=';' , header=F)
names(df) <- c("Name","Gender" , "count")
head(df)

# 1.b summary of df

summary(df)

 #     structure of df

str(df)

# 1.c  finding duplicate entry

grep("yyy$" , df$Name , value=TRUE)

#  1.d remove the redundant entry

y2016 <- df[-1*which(df$Name == (grep("yyy$" , df$Name , value=TRUE))),]
str(y2016)
```


### Question2 - Data Merging \

Dataset used  - yob2015.txt \
Description   - This file is a series of popular children's names born in the year 2015 in the United States. \
variables     - firstname,gender,amount of children given that name \

```{r datamerging,echo=TRUE}

#  2.a  import given dataset into R dataframe y2015

y2015 <- read.table('Data/yob2015.txt', sep=',' , header=F)
names(y2015) <- c("Name","Gender" , "count")

#  2.b  display last 10 rows of the dataframe y2015
tail(y2015,10)

```
 Last 10 rows of the dataset y2015 begin with 'z' , are all names for Males and each have a total number of 5 children with the same name.
 
```{r datamergingcontd,echo=TRUE}
 
#  2.c merge dataset y2016 and y2015

final <- merge(x=y2016, y=y2015, by=union("Name","Gender"), all=FALSE)
names(final) <- c("Name", "Gender" , "count_2016" , "count_2015")
str(final)
summary(final)

```

## Question3 - Data Summary \

Dataset used - final \
Description - This dataframe is a series of popular children's names born in the year 2015 and 2016 in the United States. \
Variables - Name,Gender, count of children in the year 2016, count of children in the year 2015 \

```{r datasummary,echo=TRUE}

#  3.a  create new column Total

final$Total <- final$count_2016 + final$count_2015

#  sum of Totals gives how many people were given popular names in 2015 and 2016 combined
  
sum(final$Total)

#  3.b  sort the data by Total 

final <- final[order(final$Total,decreasing = TRUE),]

# Display top 10 popular Names

head(final,10)

#  3.c  omit names of boys 

final <- final[which(final$Gender == 'F'),]

#  Top 10 baby girl names

head(final,10)

#  3.d  write csv file to list top 10 baby girl names

write.csv(subset(head(final,10),select=c("Name","Total")),file="Data/Top10babygirlnames.csv",row.names = FALSE , col.names = TRUE )
  
```

Top 10 baby girl names file is in Data folder under the working directoy by the name *Top10babygirlnames.csv*